---
title: "Analyses"
date: "11/8/2020"
output: html_document
---

This document contains all of our analyses.

```{r setup, include=FALSE}
library(tidyverse)
library(plotly)
library(corrplot)
source("http://www.sthda.com/upload/rquery_cormat.r")
```


```{r message = FALSE, warning = FALSE}
game_df = read_csv("./data/game_2.csv") %>% 
  separate(release_date, into = c("month_day","year"), sep = ",") %>% 
  separate(genre, into = "genre", sep = ",")
```


## 1. User score vs Metascore (vs Sales)?

```{r}
game_df %>% 
  select(meta_score, user_score, total_sale) %>% 
  mutate(user_score = as.numeric(user_score)) %>% 
  rquery.cormat()
```


## 2. Total sales by genre

```{r}
game_df %>% 
  group_by(genre) %>% 
  mutate(count = n(),
         genre = str_c(genre, " (n=", count, ")")) %>%  
  ungroup() %>% 
  mutate(genre = fct_reorder(genre, total_sale),
         text_label = str_c("Title: ", title, "\nPublisher: ", publisher)) %>% 
  plot_ly(x = ~total_sale, color = ~genre, type = "box", colors = "viridis", text = ~text_label)

```


## 3. Which time period generated the most popular games?

```{r}

```


## 4. Which developers released the most/least popular games or the highest/lowest scored?

```{r}

```


## 5. Preference of users of different platform

```{r}

```


## 6. Preference of users from different regions

```{r}

```


## 7. What factors influence sales? How do they influence it?

```{r}

```

