---
title: "Final Report"
date: "11/23/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

<style type="text/css">

h1.title {
  font-size: 40px;
  font-family: 'Abel', sans-serif;
  color: #003399;
}
h1 { /* Header 1 */
  font-size: 36px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 30px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 22px;
  color: DarkBlue;
}
h4 {/* Header 4 */
  font-size: 18px;
  color: DarkBlue;
}
</style>

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(ggpubr)
library(arsenal)
library(multcomp)
library(modelr)
library(mgcv)
library(plotly)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

<br>

## Motivation

Video games have been around for decades, providing entertainment for children and adults alike. They have been involved significantly from the early days of computer games and the early versions of Nintendo and Atari. As technology continues to improve, so do video games. Video game creation has become increasingly complicated, and the cost of creating a game to run one of the major consoles has risen with this greater complexity. 

No longer just an entertainment medium, gaming has rapidly become the largest sector in terms of production and marketing. In fact, it is larger than the movie and music industry combined, and it is only growing. It is no surprise that many big companies want to bring revenues from video games. There are currently more than 2.5 billion gamers across the world. Analysts reported that in 2019, the gaming business was estimated to be at 152.1 billion in which console was the second fastest-growing segment, only after mobile gaming. It is generally known that the top largest revenue regions were Asia-Pacific, North America, and Western Europe ([source]((https://newzoo.com/insights/articles/global-games-market-reaches-137-9-billion-in-2018-mobile-games-take-half/)). In this project, we are going to analyze the 2001-2020 global games market per console from Nintendo, Sony, and Microsoft, and learn about the factors that influence their total revenues. 

<br>

## Initial Questions

In contrast to the questions we initially posed in our proposal, we decided to focus on the three major console developers and factors influencing their total sales. In other words, for games released on consoles developed by Nintendo, Sony, and Microsoft, we want to know separately:

* How do the sales of games change over time?

* What is the most popular/profitable game genre on each companies' consoles?

* Is there an association between critic scores and game sales? In which direction?

* Does the number of consoles the games are released on influence their sales?

<br> 

## Data Collection

```{r, include = FALSE}
games_df = read_csv("./data/games.csv")
```

We initially proposed to scrape most of our data from all 180 pages of games on [Metacritic](https://www.metacritic.com/browse/games/score/metascore/all/all/filtered?view=detailed&page=0) and merge them with sales data from [VGChartz](https://www.vgchartz.com/games/games.php?name=&keyword=&console=&region=All&developer=&publisher=&goty_year=&genre=Action&boxart=Both&banner=Both&ownership=Both&showmultiplat=No&results=200&order=TotalSales&showtotalsales=0&showtotalsales=1&showpublisher=0&showpublisher=1&showvgchartzscore=0&shownasales=0&shownasales=1&showdeveloper=0&showdeveloper=1&showcriticscore=0&showcriticscore=1&showpalsales=0&showpalsales=1&showreleasedate=0&showreleasedate=1&showuserscore=0&showuserscore=1&showjapansales=0&showjapansales=1&showlastupdate=0&showothersales=0&showothersales=1&showshipped=0). Metacritic is a well-known review aggregate site and is relatively transparent with its methodology for gathering critic reviews but does not contain information on sales. VGChartz is a video game sales tracking website that provides weekly sales figures of console software and hardware by region. According to their methodology page, they produce their estimates by extrapolating from retail sampling and trends, and regularly compare them to official shipment figures and figures estimated by regional trackers.

In an arduous process of figuring out how to scrape information such as genre that was only listed on the individual detail page of each game and repeatedly running into HTTP connection errors on Metacritic, we found and utilized the `polite` package to safely scrape the data without overwhelming the website. However, because some pages simply did not exist and we had ~18,000 games to scrape, the entire scraping process took over 24 hours to complete. The sales data from VGChartz was scraped relatively easily without the need of the `polite` package.

Unfortunately, after merging, our ~18,000 entries were reduced to ~2,500. We then realized that this reduction was because the two sites named many of the game titles slightly differently, and that Metacritic would list different versions of a game as separate entries while VGChartz grouped them together into one, resulting in many games that could not be merged as is. Simply dropping those entries from our dataset would be invalid, but recoding the inconsistencies manually would be entirely too time-consuming, so we decided to obtain our dataset mainly from VGChartz, possibly at the expense of having accurate critic review scores. All of the code we’ve written up to this point can be found in its own folder [here](https://github.com/fw2260/p8105_final_project/tree/main/old).

Thus our final dataset comes mainly from VGChartz, with some critic scores from the dataset mentioned above from Metacritic. Based on the raw dataset, we also created some other new columns.

The key steps for data cleaning are:

* Only keep games released on consoles by Nintendo, Sony or Microsoft using `filter`;

* Get `critic_score` from the previously scraped Metacritic dataset using `left_join` by `title` and `console`;

* Obtain the year the game was released from `release_date` using `separate`;

* Add a new column, `console_developer`, which indicates the developer of the console (Nintendo, Sony, or Microsoft);

* Add another new column, `n_platforms`, which shows the number of consoles the game was released on.

After dropping NAs, there are `r nrow(games_df)` rows and `r ncol(games_df)` columns in our final dataset.

Important variables include:

* `title`: unique title of each game

* `console`: platform on which the game was released or is playable (i.e. Switch, PS4, etc.)

* `console_developer`: company that produces the console

* `n_platforms`: number of platforms the game was released on

* `genre`: genre of the game 

* `release_year`: year of the game's release

* `critic_score`: aggregate critic review score compiled by VGChartz and Metacritic

* `total_sale`: global revenues (million $) the game earned on that particular console

The first ten rows of the dataset is as follow:

```{r}
head(games_df) %>% 
  knitr::kable(format = "html", col.names = colnames(games_df), align="c") %>%
  kableExtra::kable_styling("striped", "hover", row_label_position = "c") %>%
  kableExtra::scroll_box(width = "100%", height = "200px")
```

<br>

## Exploratory Analyses

### Global sales and Number of games released across the years{.tabset}

#### All Consoles

```{r q1, message=FALSE, warning=FALSE}
totalsale = games_df %>% 
  group_by(release_year) %>% 
  summarize(
    totalsale = sum(total_sale)
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = totalsale)) +
  geom_col(color = "navyblue", fill = "white") +
  labs(x = "Release Year", y = "Total Sale (million USD)")

totalsale_plotly = ggplotly(totalsale)

totalcount = games_df %>% 
 group_by(release_year) %>% 
  summarize(
    count = n()
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = count)) +
  geom_col(color = "darkred", fill = "white") +
  labs(x = "Release Year", y = "Number of Games")

totalcount_plotly = ggplotly(totalcount)

subplot(totalsale_plotly, totalcount_plotly, titleX = TRUE, titleY = TRUE, margin = 0.1)

```

The left bar graph shows the cumulative global revenues (in million USD) of each game by release year from 2001 and 2020 on the three companies' platforms. In other words, it is showing how much the games made (from its release year to present) by their release year. *Note: this graph is NOT showing annual sales of games.* The right graph shows the number of video games released on these platforms in the same period. 

The video game industry increased at a rapid rate after 2001 with a drastic increase in number of games released each year and the high volume reached its peak in 2008, with 620 games published on these major platforms. Presently, games generating the biggest revenue are also those released in 2008, like Grand Theft Auto IV on Xbox 360. 

Both cumulative sales and number of games released from 2008 on decreases over time, possibly reflecting the effects of the 2008 financial recession and the rise in popularity of PC and mobile gaming as technology advances. It may also be the case that console makers are not eager to release new models as often, which also decreases the number of games published each year. Furthermore, sales of more recently released games may be lower because they are younger than their predecessors. 

Additionally, note that there is a drastic drop for both sales and number of games after 2018. The number of game releases from the three companies in 2019 is only 18 and in 2020 is 5, which is not the case in reality. Therefore, we consider data in 2019 and 2020 to be inaccurate and will exclude them in our statistical analyses.

<br>

#### Nintendo

```{r, message=FALSE, warning=FALSE}
totalsale = games_df %>% 
  filter(console_developer == "Nintendo") %>% 
  group_by(release_year) %>% 
  summarize(
    totalsale = sum(total_sale)
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = totalsale)) +
  geom_col(color = "navyblue", fill = "white") +
  labs(x = "Release Year", y = "Total Sale (million USD)")

totalsale_plotly = ggplotly(totalsale)

totalcount = games_df %>% 
  filter(console_developer == "Nintendo") %>% 
  group_by(release_year) %>% 
  summarize(
    count = n()
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = count)) +
  geom_col(color = "darkred", fill = "white") +
  labs(x = "Release Year", y = "Number of Games")

totalcount_plotly = ggplotly(totalcount)

subplot(totalsale_plotly, totalcount_plotly, titleX = TRUE, titleY = TRUE, margin = 0.1)

```

We can see a similar trend for **Nintendo** and **Microsoft**. 

#### Microsoft

```{r, message=FALSE, warning=FALSE}
totalsale = games_df %>% 
  filter(console_developer == "Microsoft") %>% 
  group_by(release_year) %>% 
  summarize(
    totalsale = sum(total_sale)
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = totalsale)) +
  geom_col(color = "navyblue", fill = "white") +
  labs(x = "Release Year", y = "Total Sale (million USD)")

totalsale_plotly = ggplotly(totalsale)

totalcount = games_df %>% 
  filter(console_developer == "Microsoft") %>% 
  group_by(release_year) %>% 
  summarize(
    count = n()
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = count)) +
  geom_col(color = "darkred", fill = "white") +
  labs(x = "Release Year", y = "Number of Games")

totalcount_plotly = ggplotly(totalcount)

subplot(totalsale_plotly, totalcount_plotly, titleX = TRUE, titleY = TRUE, margin = 0.1)

```

We can see a similar trend for **Nintendo** and **Microsoft**.

#### Sony

```{r, message=FALSE, warning=FALSE}
totalsale = games_df %>% 
  filter(console_developer == "Sony") %>% 
  group_by(release_year) %>% 
  summarize(
    totalsale = sum(total_sale)
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = totalsale)) +
  geom_col(color = "navyblue", fill = "white") +
  labs(x = "Release Year", y = "Total Sale (million USD)")

totalsale_plotly = ggplotly(totalsale)

totalcount = games_df %>% 
  filter(console_developer == "Sony") %>% 
  group_by(release_year) %>% 
  summarize(
    count = n()
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = count)) +
  geom_col(color = "darkred", fill = "white") +
  labs(x = "Release Year", y = "Number of Games")

totalcount_plotly = ggplotly(totalcount)

subplot(totalsale_plotly, totalcount_plotly, titleX = TRUE, titleY = TRUE, margin = 0.1)

```

However, for **Sony**, it's a different story. Both the annual sales and number of releases starts high and then keeps decreasing.

### Global sales of games per genre

```{r q2, message=FALSE, warning=FALSE}
genre_sale_plot = 
  games_df %>% 
  group_by(genre) %>% 
  mutate(total = sum(total_sale)) %>% 
  ungroup() %>% 
  mutate(
    genre = fct_reorder(genre, desc(total))) %>% 
  group_by(genre, console_developer) %>% 
  summarise(
    sum_sale = sum(total_sale)
  ) %>% 
  ggplot(aes(x = genre, y = sum_sale, fill = console_developer)) +
  geom_bar(stat = "identity", alpha = .7) +
  theme(
    axis.text.x = element_text(angle = 70, vjust = 0.5, hjust = 1, size = 8),
    legend.position = "bottom",
    legend.text = element_text(size = 8)) +
  labs(x = "Genre", y = "Total Sale (million USD)", fill = "Console Developer")

ggplotly(genre_sale_plot) 
```

**Sports** games have been around since the beginning of gaming, and it is the most popular genre, with global sales more than 1.0 billion USD. Coming in second and third respectively are **Action** and **Shooting**, challenging the player’s reflexes and coordination. 

The revenues of each company, however, are not the same across the genres. **Nintendo** earns more profit from making games in **sports**, **role-playing**, and **platform**, with each of them bring back more than 290 million USD. **Sony**’s best-selling genre is **action**, which achieves 580.94 million USD revenue between 2001 to 2020. **Sports** and **shooting** also brings huge profits to Sony, with 481.72 and 410.72 million USD, respectively. **Microsoft**, despite being the latest competitor to enter the video game industry, performs well in the **shooting**, **sports**, and **action** genres. The company’s highest revenue is from shooting games with 403.39 million USD.  

<br>

### Relationship between critic score and total revenues

```{r q3, message=FALSE, warning=FALSE}
games_df %>% 
  filter(total_sale < 5) %>% 
  ggplot(aes(x = critic_score, y = total_sale, color = console_developer)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = 'lm', se = F) +
  labs(x = "Critic Score", y = "Total Sale (million USD)", color = "Console Developer")
```

Critic consensus on a game usually has some correlation with the success of the game in the market because critic reviews may influence consumers' decision to buy games.

Based on the fitted linear regression lines, it would seem that **Microsoft** and **Sony**'s games usually has scores greater than 5/10, which means that their games have overall good quality. While for **Nintendo**, more of its games earned low scores from critics. 

Generally though, as critic score increases, sales of games on the three companies' consoles all increase. What's interesting is that **Sony**'s game sale increases more than the others for one unit increase in critic score and **Nintendo**'s increases the least.

<br>

### Platform Availability

```{r q4, message=FALSE, warning=FALSE}
platform_available = 
  games_df %>% 
  mutate(n_platforms = as.factor(n_platforms)) %>% 
  ggplot(aes(x = n_platforms, y = log(total_sale), fill = console_developer)) +
  geom_violin(alpha = .5) +
  labs(x = "\nNumber of Platforms", y = "Total Sale Log(million USD)\n") +
  theme_light() +
  facet_wrap(~console_developer,nrow = 3) +
  theme(
    text = element_text(size = 9),
    legend.text = element_text(size = 9),
    axis.title.x = element_text(vjust = -0.5),
    axis.title.y = element_text(vjust = 3.5),
    legend.position = "none"
  )

platform_available
```

Platform availability refers to the number of consoles that a game is released on, and running more consoles indicates higher availability (e.g. you can play Grand Theft Auto V on PlayStation 4 or on Xbox One). High availability sometimes indicates high popularity, which is supposed to bring in more sales. However, non-exclusive games won't encourage people to buy certain consoles, since they can play them on consoles they already have. In this way, the sales brought by the game would be "diluted".

For games of **Microsoft** and **Sony**, the sales improves as the number of console increases overall. And this trend is more apparent for **Sony**. This means that for these two companies, more available games sells better than less available games. However, this is not the case for **Nintendo**. Even though there are also non-exclusive games on **Nintendo**'s consoles, they don't contribute more revenue than games with less platform availability. 

(Another factor that has a big impact on how well a game sales is the number of platforms the game is available. Most players do not have multiple consoles and a game that releases on multiple platforms has a much higher potential customer number. The plot showed that there was a large distribution of total revenues in the smaller number of platforms since most players owned only 1 or 2 consoles.)

<br>

## Statistical Analyses

### Anova Test

```{r, message=FALSE, warning=FALSE}
games_df = games_df %>%
   filter(release_year < 2019) %>%
  mutate(
    n_platforms = 
      case_when(n_platforms == '1' ~ 'small',
                n_platforms >= '2' & n_platforms <= '3' ~ 'medium',
                n_platforms >= '4' ~ 'large'),
    n_platforms = as.factor(n_platforms)
    ) %>% 
  dplyr::select(title:genre,critic_score, total_sale)
```
 
Using Analysis of Variance (ANOVA) we can conduct statistical comparisons among groups of our interested categorical variables: n_platforms. We further divided n_platform into 3 groups: `small` (`n_platforms` = 1), `medium` (2 <= `n_platforms` <= 3) and `large` (4 <= `n_platforms` <= 9). 
    
### 1. One-way ANOVA: total_sale ~ n_platforms 

```{r ANOVA_Genre, message=FALSE, warning=FALSE}
aov_mod_1 = aov(total_sale ~ n_platforms, data = games_df)
```
```{r }
broom::tidy(aov_mod_1)
```
```{r }
multi_comp_1 = TukeyHSD(aov_mod_1)
plot(multi_comp_1)
```

With p.value < 0.001, we conclude that at least two of the n_platforms groups have different average total_sales. Then Tukey's method was performed to make pairwise comparisons. All comparisons have significant differences in mean of total_sale.

### 2. Conclusion

The ANOVA test above provides evidence that there are true differences in games sales among different groups of n_platforms. Therefore, we will include console_developer, n_platforms, critic_score as predictors in our linear regression model.

Similarly, we conducted ANOVA test for different levels of genre and concluded that there are true difference in global sales among different genres.

<br>

### Linear Regression

```{r regression dataset, message=FALSE, warning=FALSE}
regression_df = 
  games_df %>%
  filter(total_sale < 5) # cut off outliers
```

**Need explanation here of why we decided to cut off data at this point**

### 1. Build Models

**Model 1:**  \(Model 1:  total\_sale \sim console\_developer * genre + console\_developer * n\_platforms \)

**Model 2:**  \(Model 2:  total\_sale \sim console\_developer * genre + console\_developer * n\_platforms + console\_developer * critic\_score\)

**Model 3:**  \(Model 3:  total\_sale \sim console\_developer * genre + console\_developer * critic\_score\)

**Model 4:**  \(Model 4:  total\_sale \sim console\_developer * n\_platforms + console\_developer * critic\_score\)

Model 2 contains console_developer and all other interested predictors (genre, n_platform, critic_score), as well as interactions. While Model 1, 3, and 4 contain console_developer and only two of interested predictors and their interactions. 

<br>

### 2. Cross validation

We use `crossv_mc` method to create training and testing datasets and fit the above 4 candidate models. The violin plots below shows the distribution of **RMSE** values for each model:

```{r regression_rmse_1,warning = F ,include = F}
cv_df = 
  crossv_mc(regression_df, 300) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
  
cv_df = 
  cv_df %>% 
  mutate(
    linear_1 = map(.x = train, ~lm(total_sale ~ console_developer*genre + console_developer*n_platforms, data = .x)),
    linear_2 = map(.x = train, ~lm(total_sale ~ console_developer*genre + console_developer*n_platforms + console_developer*critic_score, data = .x)),
    linear_3 = map(.x = train, ~lm(total_sale ~ console_developer*genre + console_developer*critic_score, data = .x)),
    linear_4 = map(.x = train, ~lm(total_sale ~ console_developer*n_platforms + console_developer*critic_score, data = .x))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = linear_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = linear_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = linear_3, .y = test, ~rmse(model = .x, data = .y)),
    rmse_4 = map2_dbl(.x = linear_4, .y = test, ~rmse(model = .x, data = .y))
  )
```


```{r regression_rmse_compare1234,warning = F ,message = F}
cv_df %>% 
  dplyr::select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

Based on the results, Model 2 has the lowest **RMSE**, but **RMSE** of Model 3 and 4 are just slightly higher than Model 2, which indicates that there's minor improvement for adding `console_developer*critic_score` as an additional predictor. Also, there are 6 subgroups in `genre`, which makes Model 3 harder to interpret than Model 4. In this way, we decide to select **Model 4** as our final model.

<br>

### 3. Diagnosis

In **Model 4**, we used **Residuals vs Fitted Values** plot to detect unequal error variance (heteroscedasticity) and outliers. 

```{r, message = FALSE}
lm4 = lm(total_sale ~ console_developer*n_platforms + console_developer*critic_score, data = regression_df)

regression_df %>%
  add_predictions(lm4) %>%
  add_residuals(lm4) %>%
  ggplot(aes(x = pred, y = resid))+ 
  geom_point(alpha = 0.3)+
  geom_smooth(method = 'lm', color = 'red')+
  labs(x = 'fitted values of total_sales', y = 'model residuals', title = 'Residuals vs Fitted Values')
```
  
As shown in the graph, there are many outliers with residuals > 3. Although the mean of residual values is close to 0 and residuals have a horizontal relationship with fitted value, the distribution of residual values is skewed. This plot indicates that our model does not have ideally distributed residuals.

### 4. Results

The summary of the selected model: \(Model 4:  total\_sale \sim console\_developer * n\_platforms + console\_developer * critic\_score\) is as follow:

```{r}
coe_df = broom::tidy(lm4) 

coe_df_tidy = 
  coe_df %>%
  select(term, estimate, p.value) %>% 
  mutate(
    term = str_replace(term, "^console_developer:", "Developer: "),
    term = str_replace(term, "^n_platforms:", "Num_Consoles: "),
  ) %>%
  knitr::kable(digits = 3)

coe_df_tidy
```

According to **Model 4**, with games on **Microsoft** consoles and having large console availability as reference, we can see that:

* For **Microsoft**, 

  * While controlling critic score as constant, compared to sales of game on large number of consoles, estimated sales **decreases 0.299** million USD when games run on **medium** number of consoles and **decreases 0.265** million USD when games run on **small** number of consoles; 
 
  * While controlling console availability as constant, the estimated total sales **increases 0.228** million USD for one unit increase in **critic score** on average.

* For **Nintendo**, 

  * While controlling critic score as constant, compared to sales of **Microsoft** game with same level of console availability, estimated sales **increases 0.476** million USD for **Nintendo** games with **large** number of consoles, **increases 0.691** million USD for games with **medium** number of consoles, and **increases 0.789** million USD for games with **small** number of consoles;
 
  * Among **Nintendo** games, while controlling crirtic score as constant, there is supposed to be **0.084 million USD decrease** when compared games on **medium** number of platforms with **large** number of platforms, and **0.048 million USD increase** when compared games on **small** number of platforms with **large** number of platforms;
 
  * While controlling console availability as constant, the estimated total sales **increases 0.121** million USD for one unit increase in **critic score** on average.
 
* For **Sony**, 

  * While controlling critic score as constant, compared to sales of **Microsoft** game with same level of console availability, estimated sales **decreases 0.136** million USD for **Sony** games with **large** number of consoles, **decreases 0.025** million USD for games with **medium** number of consoles, and **decreases 0.21** million USD for games with **small** number of consoles;
 
  * Among **Sony** games, while controlling critic score as constant, there is supposed to be **0.324 million USD decrease** when compared games on **medium** number of platforms with **large** number of platforms, and **0.475 million USD increase** when compared games on **small** number of platforms with **large** number of platforms;
 
  * While controlling console availability as constant, the estimated total sales **increases 0.271** million USD for one unit increase in **critic score** on average.

<br>

## Discussion

* From the analysis above, **2008** is the year with the **highest global revenues** and the **most games released**. After 2012, in general, there is a decrease in both the number of games released and total revenues for the three big companies: Nintendo, Sony, and Microsoft. 

* **Action**, **sports**, and **shooting** are the most popular genres that bring the most profits to the companies overall. 

* It seems that as critic scores increase, there is a generally associated increase in global sales as well. **Sony** is the company in which their games has the highest critic score and highest global sales. 

* Another factor that also impacts how well a game sells is the number of platforms the game is available on. Some gamers do not own multiple consoles and a game that is released on multiple platforms has a much higher potential customer base, thus higher sales. 
