---
title: "Final Report"
date: "11/23/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(ggpubr)
library(arsenal)
library(multcomp)
library(modelr)
library(mgcv)
library(plotly)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Motivation

## Initial Questions

For games run on consoles developed by Nintendo, Sony and Microsoft, we want to know separately:

* How does the sales of games change over time?

* What is the most popular/profitable game genre on each companies' consoles?

* Is there an association between critic scores and game sales? In which direction?

* Does the number of consoles the games are released on influence their sales?

## Data Collection

## Exploratory Analyses

### Question 1

```{r q1, message = FALSE}
games_df = read_csv("./data/games.csv")

totalsale = games_df %>% 
  group_by(release_year) %>% 
  summarize(
    totalsale = sum(total_sale)
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = totalsale)) +
  geom_col() +
  labs(x = "Year", y = "Total Sale (million USD)")

totalcount = games_df %>% 
 group_by(release_year) %>% 
  summarize(
    count = n()
  ) %>% 
  drop_na() %>% 
  ggplot(aes(x = release_year, y = count)) +
  geom_col() +
  labs(x = "Year", y = "Number of Games")


totalsale + totalcount
```

### Question 2

```{r q2}
games_df %>% 
  ggplot(aes(x = genre, y = total_sale, fill = console_developer)) +
  geom_bar(stat = "identity", position = "stack") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(x = "Genre", y = "Total Sale (million USD)", fill = "Console Developer")
```

### Question 3

```{r q3, message = FALSE}
games_df %>% 
  filter(total_sale < 5) %>% 
  ggplot(aes(x = critic_score, y = total_sale, color = console_developer)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = 'lm', se = F) +
  labs(x = "Critic Score", y = "Total Sale (million USD)", color = "Console Developer")
```

### Question 4

```{r q4}
games_df %>% 
  mutate(n_platforms = as.factor(n_platforms)) %>% 
  ggplot(aes(x = n_platforms, y = total_sale, fill = console_developer)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Number of Platforms", y = "Total Sale (million USD)", fill = "Console Developer")
```


## Anova Analysis
```{r }
games_df = games_df %>%
   mutate(
    genre = 
      case_when(
        genre %in% c('action','action_adventure',"adventure", "fighting") ~ 'Action',
        genre %in% c('racing','sports') ~ 'Competition',
        genre %in% c('role_playing', 'simulation') ~ 'Experience',
        genre %in% c('strategy','puzzle') ~ 'Intelligence',
        genre %in% c('platform', 'shooting')~ 'Agility',
        genre == 'miscellaneous' ~ "Miscellaneous")
    ) %>%
  mutate(
    n_platforms = 
      case_when(n_platforms == '1' ~ 'small',
                n_platforms >= '2' & n_platforms <= '3' ~ 'medium',
                n_platforms >= '4' ~ 'large'),
    n_platforms = as.factor(n_platforms)
    ) %>% 
  dplyr::select(title:genre,critic_score, total_sale)
```
 
By Analysis of Variance (ANOVA) we can conduct comparisons among groups of our interested categorical variables : genre and n_platforms.In the test of genre, we want to answer the question: Whether there are true differences in games sales among different genres? 
    
### 1. One-way ANOVA: Total_sale ~ genre 
```{r ANOVA_Genre}
aov_mod_1 = aov(total_sale ~ genre, data = games_df)
```
```{r }
broom::tidy(aov_mod_1)
```
```{r }
multi_comp_1 = TukeyHSD(aov_mod_1)
plot(multi_comp_1)
```

With p.value < 0.001, we conclude that at least two of the genres have different average total_sales. Then Tukey's method was performed to make pairwise comparisons. 7 of 15 comparisons (eg. Agility vs Competition) have significant differences in mean of total_sale.

### 2. ANOVA with interaction: Total_sale ~ console_developer * genre 

```{r }
aov_mod_2 = aov(total_sale ~ console_developer * genre, data = games_df)
```

```{r}
broom::tidy(aov_mod_2)
```

```{r }
multi_comp_2 = TukeyHSD(aov_mod_2)

ori_df = 
  broom::tidy(multi_comp_2) %>%
  filter(term == 'console_developer:genre') %>%
  na.omit() 

multi_df = 
  ori_df %>%
  filter(adj.p.value < 0.05)
```

 With p.value of the interaction term = 1.08e-9 < 0.001, we conclude that at least two of the interaction combinations have different average total_sales.From Tukey’s multiple comparisons we get that there are 36 significant different combinations among 153 combinations of console_developer and genre.
 
### 3. Conclusion: 

  Anova tests above provide us evidence that indicate there are true differences in games sales among different groups of genre. When the console_developer changes, significant differences exist in subgroups as well.  Thus it’s reasonable to include the interaction term console_developer : genre in the linear regression model.
  
  Following similar procedures, we also conclude that significant differences exist in groups of n_platform (criteria of grouping: 1 ~ small, 2-3 ~ medium, 4-9 ~ large) and subgroups considering interaction with console_developer. Therefore we include the interaction term console_developer : n_platform in the linear regression model 

## Linear Regression

### 1. Build models: 
Model 1:  total_sale ~ console_developer * genre + console_developer * n_platforms.

Model 2:  total_sale ~ console_developer * genre + console_developer * n_platforms + console_developer * critic_score

Model 3:  total_sale ~ console_developer * genre + console_developer * critic_score

Model 4:  total_sale ~ console_developer * n_platforms + console_developer * critic_score

   We set the cutoff value at 5(million dollars). Model 2 contains interaction between console_developer and all interested predictors (genre, n_platform, critic_score) while Model 1,3,4 contain interaction between console_developer and two of interested predictors. 


### 2. Cross validation:

```{r regression_rmse_1,warning = F ,include = F}
cv_df = 
  crossv_mc(regression_df, 300) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
  
  
cv_df = 
  cv_df %>% 
  mutate(
    linear_1 = map(.x = train, ~lm(total_sale ~ console_developer*genre + console_developer*n_platforms, data = .x)),
    linear_2 = map(.x = train, ~lm(total_sale ~ console_developer*genre + console_developer*n_platforms + console_developer*critic_score, data = .x)),
    linear_3 = map(.x = train, ~lm(total_sale ~ console_developer*genre + console_developer*critic_score, data = .x)),
    linear_4 = map(.x = train, ~lm(total_sale ~ console_developer*n_platforms + console_developer*critic_score, data = .x))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = linear_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = linear_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = linear_3, .y = test, ~rmse(model = .x, data = .y)),
    rmse_4 = map2_dbl(.x = linear_4, .y = test, ~rmse(model = .x, data = .y))
  )
```


```{r regression_rmse_compare1234,warning = F ,message = F}
cv_df %>% 
  dplyr::select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


### 3. Diagnosis and interpretation

  In the selected model, we used Residuals vs Fitted values plot to detect unequal error variance (heteroscedasticity) and outliers. 
```{r}
regression_df = 
  games_df %>%
  filter(total_sale < 5)
lm2 = lm(total_sale ~ console_developer*genre +  console_developer*n_platforms + console_developer*critic_score, data = regression_df)
regression_df %>%
  add_predictions(lm2) %>%
  add_residuals(lm2) %>%
  ggplot(aes(x = pred, y = resid))+ 
  geom_point(alpha = 0.3)+
  geom_smooth(method = 'lm', color = 'red')+
  labs(x = 'fitted values of total_sales', y = 'model residuals', title = 'Residuals vs fitted values')
```
  
  
  As shown in the graph, there are many outliers with residuals > 3. Although the mean of residual values is close to 0 and residuals have a horizontal relationship with fitted value, the distribution of residual values is skewed. This plot indicates that our model does not have ideally distributed residuals.
  make jeff's table
```{r}
coe_df = broom::tidy(lm2) 
coe_df1 = coe_df[-c(2:11),] %>%
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^console_developerNintendo:", "Nintendo: "),
         term = str_replace(term, "^console_developerSony:", "Sony: "),
  ) %>%
  knitr::kable(digits = 3)
coe_df1
```

  We compare coefficients of interaction terms between console_developer and genre/n_platforms/critic_score in the first table. (For example, console_developerNintendo:genreAgility is separated into row name-genreAgility and column name-console_developerNintendo.)
  
  Interpretation:
  
```{r}
coe_df = broom::tidy(lm2) 
coe_df2 = coe_df[c(1:11),] %>%
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
coe_df2
```
 
  In the second table, coefficients of single terms such as genreAgility, genreCompetition are shown.
  
  Interpretation: