---
title: "Tidy Sales Data"
date: "11/10/2020"
output: github_document
---

This document contains steps to clean the sales data.

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
```


Load sales data, remove `m` in each sale column, and change "N/A" to NA

```{r}
#sales_data = 
#  read_csv("data/sales.csv") %>% 
#  separate(total_sale, into = c("total_sale", NA), sep = "[m]") %>% 
#  separate(na_sale, into = c("na_sale", NA), sep = "[m]") %>% 
#  separate(pal_sale, into = c("pal_sale", NA), sep = "[m]") %>% 
#  separate(japan_sale, into = c("japan_sale", NA), sep = "[m]") %>% 
#  separate(other_sale, into = c("other_sale", NA), sep = "[m]")

# a shorter one. It also works!

sales_data = 
  read_csv("./data/sales.csv") %>%
  janitor::clean_names() %>% 
  mutate_at(3:7, funs(gsub("m$","",.))) %>% 
  mutate_at(3:7, funs(gsub("N/A",NA,.)))
```


To list the unique name of console.

```{r}
sales_data %>% 
  distinct(console)
```

There are `r sales_data %>% distinct(console) %>% nrow` unique consoles listed. 

Rename console in sales data

**NOTE: The following console cannot be found to match in the `metacritic.csv` file: 2600, GBC, GEN, PSN, SAT, SCD, WS, VC, NG, WW, PCE, XBL, 3D0, GG, OSX, PCFX, Mob


```{r}
sales_df = 
  sales_data %>% 
  mutate(
    console = 
      recode(console, 
       PS = "PlayStation",
       PS2 = "PlayStation 2",
       PS3 = "PlayStation 3",
       PS4 = "PlayStation 4",
       GB = "Game Boy Advance",
       X360 = "Xbox 360",
       NS = "Switch",
       N64 = "Nintendo 64",
       XOne = "Xbox One",
       XB = "Xbox",
       WiiU = "Wii U",
       GC = "GameCube",
       PSV = "PlayStation Vita",
       DC = "Dreamcast"
       )
  ) %>% 
  rename(platform = console)

 
```

#New name for console values

write the new sales dataset into a .csv file
```{r}
#sales_df = 
#  sales_data %>% 
#  mutate(console = console_df) %>% 
#  rename(platform = console)

write_csv(sales_df, "./data/sales_rename_2.csv")
```

Merge the Metacritic dataset and the sales dataset

```{r}
sales_rename = read_csv("./data/sales_rename_2.csv")
metacritic = read_csv("data/metacritic.csv")

game_df = 
  left_join(metacritic, sales_rename, by = c("title", "platform"))

write_csv(game_df, "./data/game_2.csv")

```

