---
title: "Tidy VGChartz"
date: "11/19/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Merge datasets

```{r}
game_df = 
  tibble(
    path = list.files("data/genre_sales")) %>% 
  mutate(genre = str_extract(path, "[^.]+"),
         path = str_c("data/genre_sales/", path),
         data = map(.x = path, ~read_csv(.x))) %>% 
  unnest(data) %>% 
  select(-path) %>% 
  select(title, console, genre, release_date, everything()) %>%              mutate_at(9:13, funs(gsub("m","",.))) %>% 
  mutate_at(7:13, funs(gsub("N/A",NA,.))) %>% 
  mutate_at(7:13, funs(as.numeric(.))) %>% 
  mutate(release_date = lubridate::dmy(release_date)) %>% 
  distinct() %>% 
  filter(total_sale != 0) %>% 
  filter(!is.na(total_sale)) 

write_csv(game_df, "./data/vgchartz.csv")
```

## Import Data

```{r}
vgc_data = read_csv("./data/vgchartz.csv")
```

then recode the console names

```{r}
vgc_data = 
  vgc_data %>% 
 mutate(
     console = recode(console, 
       PS = "PlayStation",
       PS2 = "PlayStation 2",
       PS3 = "PlayStation 3",
       PS4 = "PlayStation 4",
       PSP = "PlayStation Portable",
       PSN = "PlayStation Network",
       GBA = "Game Boy Advance",
       GB = "Game Boy",
       GBC = "Game Boy Color",
       X360 = "Xbox 360",
       NS = "Switch",
       N64 = "Nintendo 64",
       XOne = "Xbox One",
       XB = "Xbox",
       XBL = "Xbox Live",
       WiiU = "Wii U",
       GC = "GameCube",
       PSV = "PlayStation Vita"
       )
  ) %>% 
   mutate(
    genre = 
      case_when(
        genre %in% c('action','action_adventure',"adventure", "fighting") ~ 'Action',
        genre %in% c('racing','sports') ~ 'Competition',
        genre %in% c('miscellaneous','role_playing', 'simulation') ~ 'Experience',
        genre %in% c('strategy','puzzle') ~ 'Intelligence',
        genre %in% c('platform', 'shooting')~ 'Agility')
    )
```


## Deal with NAs

Inspect NAs in each columns

```{r}
vgc_data %>% 
  sapply(., function(x) sum(is.na(x)))
```

There are NAs in some columns, especially in user_score, there are 17291 NAs, which `r round((17291/nrow(vgc_data))*100, digits = 2)`%.

Inspect NAs in each genre.

```{r}
vgc_data %>% 
  group_by(genre) %>% 
  summarise(
    n_na = sum(is.na(critic_score)),
    pct_na = n_na/n()) %>% 
  knitr::kable()
```

We can see that the percentage of NAs in each genre is quite high and uniform.

Replace NAs in regional sales with 0, drop user_score, and drop NAs in other columns

```{r}
vgc_score_1 = 
  vgc_data %>% 
  select(-user_score) %>%
  drop_na(release_date, critic_score) %>% 
  mutate_at(
    vars(ends_with("sale")),
    ~replace(.,is.na(.), 0)
  ) 
```

Get meta_score from metacritic dataset

```{r}
metacritic_df = read_csv("./old/data/metacritic.csv")

metacritic_score = 
  metacritic_df %>% 
  rename(
    critic_score = meta_score,
    console = platform) %>% 
  select(title,console, critic_score) %>% 
  mutate(
    critic_score = critic_score/10
  )

vgc_score_2 =
  vgc_data %>% 
  select(-user_score) %>% 
  drop_na(release_date) %>% 
  mutate_at(
    vars(ends_with("sale")),
    ~replace(.,is.na(.), 0)
  ) %>% 
  filter(is.na(critic_score)) %>% 
  select(-critic_score) %>% 
  left_join(metacritic_score, by = c("title","console")) %>% 
  relocate(critic_score, .after = developer) %>% 
  filter(!is.na(critic_score))
 
vgc_data = 
  vgc_score_1 %>% 
  bind_rows(vgc_score_2)
   
```


## Tidy Data

Get released year and omit released month and day

```{r}
vgc_tidy = 
  vgc_data %>%
  separate(
    release_date, into = c("release_year", "release_month", "release_day"), sep = "-", remove = TRUE
  ) %>% 
  mutate(
    release_year = as.numeric(release_year)
  ) %>% 
  select(-release_month, -release_day) 
```

Add new columns: the number of consoles that each game was on and consoles' developers 

```{r}
n_plf_df = 
  vgc_tidy %>% 
  group_by(title) %>% 
  summarise(
    n_platforms = n(),
  ) 
  
vgc_new = 
  vgc_tidy %>% 
  left_join(n_plf_df, by = "title") %>% 
  relocate(n_platforms, .after = console) %>% 
  mutate(console_developer = 
           case_when(
                      console == 'SNES' ~ 'Nintendo',
                      str_detect(console,"^Wii") ~ "Nintendo",
                      str_detect(console,"^Game") ~ "Nintendo",
                      str_detect(console,"^N") ~ "Nintendo",
                      str_detect(console,"DS$") ~ "Nintendo",
                      str_detect(console,"^PlayStation")~"Sony",
                      str_detect(console,"^Xbox") ~ "Microsoft"
                                 ),
         console_developer = as.factor(console_developer)
        ) %>% 
   relocate(console_developer, .after = console) 
```

Only include games which were on consoles developed by Nintendo, Sony and Microsoft, and games released after 2001 (the time when Microsoft started developing consoles)

```{r}
vgc_df =
vgc_new %>% 
  filter(!is.na(console_developer)) %>% 
  filter(release_year >= 2001) 
```

## Export Dataset

```{r}
write_csv(vgc_df, "./data/games.csv")
```
