---
title: "Webscraping"
date: "11/3/2020"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)
```

<<<<<<< HEAD
Scrape from home pages
=======
Scrape the game title, release date, platform, metascore, and user score from all 180 pages:
>>>>>>> 8245790c3573851bbb7528ac6ba212d823307f4d

```{r}
title_vec = c()
platform_vec = c()
release_date_vec = c()
meta_score_vec = c()
user_score_vec = c()

for (i in 0:10) {
url = paste("http://www.metacritic.com/browse/games/score/metascore/all/psvita/filtered?view=detailed&page=", i, sep = "")

metacritic_html = read_html(url)

title =
  metacritic_html %>% 
  html_nodes(".title h3") %>% 
  html_text()
  
title_vec = append(title_vec, title[-1])

platform = 
  metacritic_html %>% 
  html_nodes(".platform .data") %>% 
  html_text() %>% 
  gsub("\n","",.)  %>% 
  gsub("^\\s+|\\s+$","",.) 
  

platform_vec = append(platform_vec,platform)

release_date = 
  metacritic_html %>% 
  html_nodes(".platform+ span") %>% 
  html_text()

release_date_vec = append(release_date_vec,release_date)

meta_score = 
  metacritic_html %>% 
  html_nodes(".clamp-metascore .positive") %>% 
  html_text()

meta_score_vec = append(meta_score_vec,meta_score)

user_score = 
  metacritic_html %>% 
  html_nodes(".user") %>% 
  html_text()

user_score_vec = append(user_score_vec,user_score)
}


```

<<<<<<< HEAD
Create a table to store all variables.
=======

Create a tibble to store all variables:
>>>>>>> 8245790c3573851bbb7528ac6ba212d823307f4d

```{r}
games_df <- tibble(
  title = title_vec,
  platform = platform_vec,
  release_date = release_date_vec,
  meta_score = meta_score_vec,
  user_score = user_score_vec
  )
```
<<<<<<< HEAD

Scrape from detail pages

```{r}
platform_add = tolower(platform_vec) %>% 
  str_replace_all(" ","-")
  
title_add = tolower(title_vec) %>% 
  str_replace_all(":","") %>% 
   str_replace_all("'","") %>% 
   str_replace_all(" /","") %>% 
   str_replace_all(";","") %>% 
   str_replace_all("\\(","") %>% 
   str_replace_all("\\)","") %>% 
   str_replace_all("\\.","") %>% 
   str_replace_all("\\ &","") %>%
   str_replace_all("\\$","") %>% 
  str_replace_all(",","") %>% 
   str_replace_all(" ","-")  

developer_vec = c()
 
  for (i in 1:400) {
  url = paste("https://www.metacritic.com/game",platform_add[i],title_add[i],sep = "/")
  tryCatch({
    detail_html = read_html(url)
    developer = 
    detail_html %>% 
    html_nodes(".developer .data") %>% 
    html_text() %>% 
    gsub("\n","",.)  %>% 
    gsub("^\\s+|\\s+$","",.)
    developer_vec = append(developer_vec,developer)},
           error = function(e) print(i))
    } 


```



=======
>>>>>>> 8245790c3573851bbb7528ac6ba212d823307f4d
