---
title: "Metacritic scrape"
date: "11/6/2020"
output: github_document
---

**WARNING:** The following code (specifically the second half) may take over 24 hours to run.

Some websites limit the number of requests that can be made in a time period and the user will experience HTTP connection errors if they make requests too quickly. The `polite` package is used to safely and respectfully scrape data from websites.

The Metacritic site is constantly updating as new games are released, so the dataset we use in our analyses is the latest version as of the morning of 11/10/2020. 

```{r setup}
library(tidyverse)
library(rvest)
library(polite)
```

Scrape the title, hyperlink of the title, platform, release date, Metascore, and user score from the main Metacritic "Game Release by Score" page:

```{r main_page, eval = FALSE}
title_vec = c()
link_vec = c()
platform_vec = c()
release_date_vec = c()
meta_score_vec = c()
user_score_vec = c()

for (i in 0:179) {
  message("Scraping pg ",i)
  url = paste("http://www.metacritic.com/browse/games/score/metascore/all/psvita/filtered?view=detailed&page=", i, sep = "")

  metacritic_html = bow(url, force = TRUE)

  link = scrape(metacritic_html) %>% 
  html_nodes(".title") %>% 
  html_attr("href")
  link_vec = append(link_vec, link) %>% 
  na.omit()

  title = scrape(metacritic_html) %>% 
  html_nodes(".title h3") %>% 
  html_text() 
  
  title_vec = append(title_vec, title[-1])

  platform = 
    scrape(metacritic_html) %>% 
    html_nodes(".platform .data") %>% 
    html_text() %>% 
    gsub("\n","",.)  %>% 
    gsub("^\\s+|\\s+$","",.) 
  
  platform_vec = append(platform_vec,platform)

  release_date = 
    scrape(metacritic_html) %>% 
    html_nodes(".platform+ span") %>% 
    html_text()
  
  release_date_vec = append(release_date_vec,release_date)
  
  meta_score = 
    scrape(metacritic_html) %>% 
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "clamp-metascore", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "positive", " " ))]|//*[contains(concat( " ", @class, " " ), concat( " ", "clamp-metascore", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "mixed", " " ))]|//*[contains(concat( " ", @class, " " ), concat( " ", "clamp-metascore", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "negative", " " ))]') %>% 
    html_text() 
  
  meta_score_vec = append(meta_score_vec,meta_score)
  
  user_score = 
    scrape(metacritic_html) %>% 
    html_nodes(".user") %>% 
    html_text()
  
  user_score_vec = append(user_score_vec,user_score)
  }

```


Enter each individual game's detail page to scrape developer, publisher, genre, and ESRB rating:

```{r detail_pages, eval = FALSE}
developer_vec = c()
genre_vec = c()
esrb_rating_vec = c()
publisher_vec = c()
 
for (i in 1:length(link_vec)) {
  message("scraping link ",i)
  url = paste("https://www.metacritic.com", link_vec[i], sep = "")
  detail_html = bow(url, force = TRUE)
    
  developer = 
    scrape(detail_html) %>% 
    html_nodes(".developer .data") %>% 
    html_text() %>%       
    ifelse(length(.) == 0, NA, .) %>% 
    gsub("\n","",.)  %>% 
    gsub("^\\s+|\\s+$","",.)
    
  developer_vec = append(developer_vec,developer)
  
  publisher = 
    scrape(detail_html) %>% 
    html_nodes(".publisher a") %>% 
    html_text() %>% 
    ifelse(length(.) == 0, NA, .) %>% 
    gsub("\n","",.) %>% 
    gsub("^\\s+|\\s+$","",.)
  publisher_vec = append(publisher_vec, publisher)
    
  genre = 
    scrape(detail_html) %>% 
    html_nodes(".product_genre") %>% 
    html_text() %>% 
    ifelse(length(.) == 0, NA, .) %>% 
    gsub("\n","",.) %>% 
    str_remove("Genre\\(s\\):") %>% 
    str_squish()

  genre_vec = append(genre_vec,genre)

  esrb_rating = 
    scrape(detail_html) %>% 
    html_nodes(".product_rating .data") %>% 
    html_text() %>% 
    ifelse(length(.) == 0, NA, .) %>% 
    gsub("\n","",.)

  esrb_rating_vec = append(esrb_rating_vec,esrb_rating)
  message("Length of vector is ",length(genre_vec))
}
```


Put all scraped data into one dataframe and output it as a csv:

```{r eval = FALSE}
games_df = tibble(
  title = title_vec,
  link = link_vec,
  platform = platform_vec,
  release_date = release_date_vec,
  meta_score = meta_score_vec,
  user_score = user_score_vec,
  developer = developer_vec,
  publisher = publisher_vec,
  genre = genre_vec,
  esrb_rating = esrb_rating_vec)

write_csv(games_df, "data/metacritic.csv")
```

